Visualization of [fulle name] Fractional Integrals

### 2019-04-17 fractional/CMJ style files/article-template.tex
made improvements to example section --- still lots todo

Let us first consider the following fractional integral:
\begin{equation}
\label{eq:ex1_raw}
\frac{1}{\Gamma(\alpha)}\int_0^t f(\tau) (t-\tau)^{\alpha-1}~d\tau = \frac{1}{\Gamma(\alpha)}\int_0^t \tau(t-\tau)^{\alpha-1}~d\tau. 
\end{equation}
We can assign a geometric interpretation to the above fractional integral by converting it into a Cavalieri integral using two steps. First, we convert 
the above integral into a Riemann-Stieltjes integral:
\begin{equation}
\frac{1}{\Gamma(\alpha)}\int_0^t f(\tau) (t-\tau)^{\alpha-1}~d\tau = \int_0^t f(\tau)~dg_t^{\alpha}(\tau). 
\end{equation}
We then convert the resulting Riemann-Stieltjes integral into a Cavalieri integral:
\begin{equation}
\label{eq:ex1}
\frac{1}{\Gamma(\alpha)}\int_0^t f(\tau) (t-\tau)^{\alpha-1}~d\tau = \int_0^t f(\tau)~dg_t^{\alpha}(\tau)=\int_{a_t^{\alpha}(y)}^{b_t^{\alpha}(y)} f(\tau)~d\tau. 
\end{equation}
We know that a Cavalieri integral can be interpreted as the area which is obtained by summing together the area associated with an infinite number of non-rectangular infinitesimals whose shape 
is determined by the integration limits of the Cavalieri integral. Note that neither $g_t^{\alpha}(\tau)$ nor $a_t^{\alpha}(y)$ are static functions, 
they depend on the value of $\alpha$ and $t$. This implies that a fractional integral of order $\alpha$ and extent $t$ can be interpeted as the area obtained by summing together the area associated with an infinite number of infinitesimals whose 
shape is determined by $\alpha$ and $t$, i.e. the geometric interpretation of Eq.~\eqref{eq:ex1_raw} is non-static as it depends on the value of $\alpha$ and $t$.

Lets clarify the above by working through a detailed example. If we set the value of $\alpha$ to $\frac{4}{5}$ and the value of $t$ to 10 in Eq.~\eqref{eq:ex1} we obtain:
\begin{equation}
\int_{a_{10}^{\frac{4}{5}}(y)}^{b_t^{\alpha}(y)} f(\tau)~d\tau. 
\end{equation}
This integral can be interpreted as the area of the region bounded by the $x$-axis, the function $f(y)$ and the function $b_{10}^{\frac{4}{5}}(y)$. Let us denote 
this region with the symbol $R_1$. The region $R_1$ is depicted and labelled in the left most panel of Figure.~\ref{??}. The function

>>>>

Let us first consider the following fractional integral:
\begin{equation}
\label{eq:ex1_raw}
\frac{1}{\Gamma(\alpha)}\int_0^t f(\tau) (t-\tau)^{\alpha-1}~d\tau = \frac{1}{\Gamma(\alpha)}\int_0^t \tau(t-\tau)^{\alpha-1}~d\tau. 
\end{equation}
The function $f(\tau) =\tau$ is depicted in Figure~\ref{??}. We can assign a geometric interpretation to the above fractional integral by converting it into a Cavalieri integral using two steps. First, we convert 
the above integral into a Riemann-Stieltjes integral:
\begin{equation}
\frac{1}{\Gamma(\alpha)}\int_0^t f(\tau) (t-\tau)^{\alpha-1}~d\tau = \int_0^t f(\tau)~dg_t^{\alpha}(\tau). 
\end{equation}
We then convert the resulting Riemann-Stieltjes integral into a Cavalieri integral:
\begin{equation}
\label{eq:ex1}
\frac{1}{\Gamma(\alpha)}\int_0^t f(\tau) (t-\tau)^{\alpha-1}~d\tau = \int_0^t f(\tau)~dg_t^{\alpha}(\tau)=\int_{a_t^{\alpha}(y)}^{b_t^{\alpha}(y)} f(\tau)~d\tau. 
\end{equation}
We know that a Cavalieri integral can be interpreted as the area which is obtained by summing together the area associated with an infinite number of non-rectangular infinitesimals whose shape 
is determined by the integration limits of the Cavalieri integral. Note that neither $g_t^{\alpha}(\tau)$ nor $a_t^{\alpha}(y)$ are static functions, 
they depend on the value of $\alpha$ and $t$. This implies that a fractional integral of order $\alpha$ and extent $t$ can be interpeted as the area obtained by summing together the area associated with an infinite number of infinitesimals whose 
shape is determined by $\alpha$ and $t$, i.e. the geometric interpretation of Eq.~\eqref{eq:ex1_raw} is non-static as it depends on the value of $\alpha$ and $t$.

Lets clarify the above by working through a detailed example. If we set the value of $\alpha$ to $\frac{4}{5}$ and the value of $t$ to 10 in Eq.~\eqref{eq:ex1} we obtain:
\begin{equation}
\int_{a_{10}^{\frac{4}{5}}(y)}^{b_{10}^{\frac{4}{5}}(y)} f(\tau)~d\tau. 
\end{equation}
This integral can be interpreted as the area of the region bounded by the $x$-axis, the function $f(\tau)$ and the function $b_{10}^{\frac{4}{5}}(y)$. Let us denote 
this region with the symbol $R_{10}^{\frac{4}{5}}$. The region $R_{10}^{\frac{4}{5}}$ is depicted and labelled in the right-most panel of Figure.~\ref{??}. We are now in a position to assign a geometric 
interpretaion to Eq.~\eqref{}. We can approximate the area of $R_{10}^{\frac{4}{5}}$
by summing together the area of non-rectangular integration strips that inscribe $R_{10}^{\frac{4}{5}}$. The only resctriction being: the sides of these non-rectangualar integration strips have to be translations of $b_{10}^{\frac{4}{5}}(y)$.
Lets now choose to approximate the area of $R_{10}^{\frac{4}{5}}$ using five integration strips of equal width. The aformentioned integration strips are depicted in the right-most panel of Figure~\ref{??}.
The sides of the integration strips are depicted using dashed lines. The more integration strips we consider the better our approximation of $R_{10}^{\frac{4}{5}}$ becomes.

We can better approximate the area of $R_{10}^{\frac{4}{5}}$ by increasing the number of integrations strips we use .   Increasing the number of integration strips we use improves our approximation of the area of $R_{10}^{\frac{4}{5}}$  
If we decide on using five integration strips

that 
we use whose sides are translations of $b_{10}^{\frac{4}{5}}(y)$

Each panel of 
Figure~\ref{??} depicts the function $f(\tau)$ and the set of curves $\mathsf{B}_T^{\alpha}$. The set $\mathsf{B}_T^{\alpha}$ is defined in Table~\ref{??} and contains 
all the Cavalieri integral upper limits obtained by fixing the order of integration $\alpha$ to a specific value. In each panel, we depict the set of curves $\mathsf{B}_T^{\alpha}$ using different shades of grey. 
The shade with which $b_t^{\alpha}(y)$ is depicted becomes lighter as the value of $t$ increases.

The The $y$-valued functions are depicted in different shades of gray. The $\tau$-valued fun

The curve in the rightmost panel of 
Figure~\ref{} which is depicted in the lightest shade of gray of

The function $b_{10}^{\frac{4}{5}}(y)$ 
depicted in the lightest shade of gray used within the right-most panel

The right-most panel of Figure.~\ref{??} contains 
a few $y$-valued curves, each one depicted in a different shade of gray. The curve depicted in the lightest shade of gray is

In each of the panels  curves $\mathsf{B}_1^{\alpha}$
